Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-23 GWLDCII.tex
last of things we discussed together

As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope. However, each individual tree level integral has singularities. These singularities are of two types physical and spurious.  The physical singularities come from special kinematical points and we will not consider them in this paper.  The spurious singularities come from zeros of the denominator, and hence are accessible to our combinatorial techniques.  SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.  Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how this works is unclear. The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.

@@

Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace. We show that given the \hlfix{physically correct}{This was here before but can you remind me what it is hinting at?}\sanote{This  is awkward. I think I meant that there are many representations of the positroid cell; wwe want thhe representattion that is  good for the physics.} representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace. This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.

>>>>

As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope. However, each individual tree level integral has singularities. These singularities are of two types: physical and spurious.  The physical singularities come from special kinematical points and we will not consider them in this paper.  The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.  SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.  Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear. The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.

@@

Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace. We show that given the representation of the positroid cell associated to an admissible Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace. This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
